\documentclass[12pt,letterpaper,roman,english]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage[scale=0.75,a4paper]{geometry}
\usepackage{babel}
%----------------------------------------------------------------------------------
%            personal data
%----------------------------------------------------------------------------------
\firstname{Ivan Fernando}
\familyname{Galaviz Mendoza}
%\title{Resumé title}                               % optional, remove/comment the line if not wanted
%\address{Matamoros 339}{44450}{México}         % optional, remove/comment the line if not wanted; the "country" arguments can be omitted or provided empty
\mobile{+52 (133) 1234-0239}                          % optional, remove/comment the line if not wanted
%\phone{phone number}                           % optional, remove/comment the line if not wanted
%\fax{fax number}                             % optional, remove/comment the line if not wanted
\email{galavizivan23@gmail.com}                               % optional, remove/comment the line if not wanted
\homepage{www.linkedin.com/in/ivanovishado}       % optional, remove/comment the line if not wanted
\social[github]{ivanovishado}
%\extrainfo{}                 % optional, remove/comment the line if not wanted
% \photo[64pt][0.4pt]{picture}                       % optional, uncomment the line if wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
\quote{A human being passionate about developing tools that will enhance human-computer interactions.}                                 % optional, remove/comment the line if not wanted
%
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle
\section{Experience}
\cventry{November 2019--Present}{Software Engineer II}{Wizeline}{Guadalajara, Mexico}{}{
	>> Currently developing significant features for one of the biggest broadcasting clients of the U.S.\newline
	>> Give courses to the community about programming languages, trying to identify potential engineers and motivate them to start their journey in the IT industry.\newline
	>> Making continuing efforts to begin my career on Data Science.
}
\cventry{November 2018--
	October 2019}{Software Engineer}{Wizeline}{Guadalajara, Mexico}{}{
	>> Developed many features of a chatbot for one of the company's biggest customers.\newline
	>> Contributed sporadically to the platform that manages all the chatbots from Wizeline.\newline
	>> Gave courses to High School students to implement chatbots easily.
}
\cventry{August 2018--
	October 2018}{Software Engineer Trainee}{Wizeline}{Guadalajara, Mexico}{}{Worked as a Full-Stack Web Developer in the most used internal project. Developed significant new features and refactored a lot of legacy code.}

\section{Education}
\cventry{2013 -- 2018}{Bachelor of Computer Engineering}{University of Guadalajara}{}{}{
	>> Terminal Project: News scraper for Mexican news websites. Scrapes news on a daily basis from $\sim$10 newspapers of each state of Mexico, has a web app that lets a user query for desired news and classifies news, as violent or non-violent, according to their content.\newline
	Try to make a search at \url{http://turing.iimas.unam.mx/news-scraper/}
}  % arguments 3 to 6 can be left empty
\cventry{Summer 2018}{Summer Research Internship "Programa Delfín"}{National Polytechnic Institute}{Mexico City}{}{Helped during the development of an emotion detector software for social networks.}
\cventry{Summer 2017}{Summer Research Internship "Programa Delfín"}{Research Institute of Applied Mathematics and in Systems, UNAM}{Mexico City}{}{Applied many technologies related to chatbots, the main project was to create a chatbot "Linguabot+, an adviser chatbot for the practice of the English Language," to help people improve their English on Facebook. It helped around 15 people to improve their English and experience with computer programs.}
%\cventry{year--year}{Degree}{Institution}{City}{Grade}{Description}
%\section{Master thesis}
%\cvitem{title}{Title}
%\cvitem{supervisors}{Supervisors}
%\cvitem{description}{Short thesis abstract}
%\section{Experience}
%\subsection{Vocational}
%\cventry{year--year}{Job title}{Employer}{City}{}{General description no longer than 1--2 lines}
%\cventry{year--year}{Job title}{Employer}{City}{}{General description no longer than 1--2 lines}
%\subsection{Miscellaneous}
%\cventry{year--year}{Job title}{Employer}{City}{}{General description no longer than 1--2 lines}

\section{Volunteer Experience}
\cventry{February 2019--
	Present}{Mentor}{Technovation Challenge}{Guadalajara, Mexico}{}{Successfully mentored two teams, one at the High School level and the other one at the Jr. High School, to develop mobile applications to contribute to their community by solving social problems.}
\cventry{January 2018--
	Present}{Software Developer Volunteer}{Research Institute of Applied Mathematics and in Systems, UNAM}{Remote fashion}{}{Developing a news scraper for Mexican news websites.}
\cventry{January 2018--
	November 2018}{Data Analyst Volunteer}{University of Guadalajara}{}{}{
	>> Analyzed data collected from students, looking to improve academic courses.\newline
	>> Created a system that lets a user recollect data from surveys semi-automatically.\newline
	>> Helped with managing courses and delivering homework notes to students.}

\section{Honors \& Awards}
\cvitem{2018}{Awarded "Award to the Performance Excellence EGEL-Ceneval": National award given yearly to the top 2\% students in the country that take the CENEVAL-EGEL exam.}
\cvitem{Summer 2018}{Scholarship awarded by the University of Guadalajara to attend the Summer Internship "Programa Delfín" in 2018 at the National Polytechnic Institute and its congress afterwards.}
\cvitem{2017}{Beneficiary of the program "Jóvenes de Excelencia" by Citibanamex which supports the application to a master's degree program abroad.}
\cvitem{Summer 2017}{Scholarship awarded by the University of Guadalajara to attend the Summer Internship "Programa Delfín" in 2017 at the Research Institute of Applied Mathematics and in Systems, UNAM and its congress afterwards.}
\cvitem{Winter 2015}{Scholarship awarded by the University of Guadalajara to go abroad for a month to study English.}

\section{Skills}
\cvitem{Soft Skills}{Teamwork, Proactiveness, Effective Communication, Emotion Understanding}
\cvitem{Programming Languages}{Python, Golang, Javascript, Java, C++, SQL}
\cvitem{Frameworks}{Flask, Node.js, React.js}
\cvitem{ORMs}{Sequelize, PyMongo, SQLAlchemy}
\cvitem{Tools}{Git, Visual Studio, PyCharm, IntelliJ IDEA, Eclipse, Netbeans, Redis}

\section{Languages}
\cvitem{English}{IELTS Academic (Score: 7.0)}
%\section{Interests}
%\cvitem{Hobby 1}{Description}
%\cvitem{Hobby 2}{Description}
%\cvitem{Hobby 3}{Description}

\section{Congresses}
\cventry{August 2018}{Speaker}{Technological University of Bahia de Banderas}{Nuevo Vallarta}{}{Described the project I helped with at my 2018 internship "Negative emotion detector for Social Networks."}
\cventry{August 2017}{Speaker}{Bahia de Banderas Institute of Techonology}{Bahía de Banderas}{}{Described the project I helped with at my 2017 internship "Adviser Chatbot for the practice of the English Language."}

\section{Languages}
\cvitem{English}{IELTS Academic (Score: 7.0)}

\section{Courses}
\cventry{Winter 2015}{English PLUS -- English Language Program}{University of Toronto}{}{A+}{Interacted with people from a diverse variety of cultures and learned more about the city and its whereabouts on a daily basis.}

%\clearpage
%-----       letter       ---------------------------------------------------------
% recipient data
%\recipient{Company Recruitment team}{Company's name\\Street address\\Zip Code City}
%\date{Date}
%\opening{Dear Sir or Madam,}
%\closing{Yours faithfully,}
%\enclosure{enclosures}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
%\makelettertitle
%\makeletterclosing
\end{document}
