%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Bachelor of Computer Engineering} % Degree
    {University of Guadalajara} % Institution
    {Guadalajara, Mexico} % Location
    {Aug. 2013 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Terminal Project: I made a news scraper for Mexican news websites. It scrapes news daily from around 10 newspapers of each state of Mexico, has a web app that lets a user query for desired news, and classifies news as violent or non-violent, according to their content.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Engineering Bootcamp} % Degree
    {Wizeline Academy} % Institution
    {Guadalajara, Mexico} % Location
    {Oct. 2021 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {I participated in a Data Engineering Bootcamp, where I learned state-of-the-art techniques and tools that professional Data Engineers use in top companies.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Summer Research Internship "Programa Delfín"} % Degree
    {National Polytechnic Institute} % Institution
    {Mexico City} % Location
    {Summer 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Helped during the development of an emotion detector classifier for social networks.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Summer Research Internship "Programa Delfín"} % Degree
    {Research Institute of Applied Mathematics and in Systems, UNAM} % Institution
    {Mexico City} % Location
    {Summer 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Created a chatbot that helped around 15 people to improve their English and experience with computer programs.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
