%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Netflix} % Organization
    {Guadalajara, Mexico} % Location
    {Apr. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Building a Digital Asset Management (DAM) System that powers marketing campaigns for Netflix titles worldwide.}
        \item {Collaborating with cross-functional teams to deliver scalable solutions reaching millions of users.}
        \item {Skills: Distributed Systems · Java · Microservices}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Nubank} % Organization
    {Guadalajara, Mexico} % Location
    {Aug. 2021 - Apr. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the design, implementation, and monitoring of critical projects to enhance the experience of people applying for Nubank's products.}
        \item {Collaborated and coordinated with different stakeholders among several teams to achieve success in our assigned projects.}
        \item {Mentored Mid engineers to empower them to own important tasks and projects.}
        \item {Interviewed dozens of candidates along all the steps in the hiring pipeline, from reviewing take-home challenges to on-site sessions.}
        \item {Planned, organized, and executed initiatives to increase brand awareness (Building Nu MX Meetups.)}
        \item {Skills: Functional Programming · Datomic · Event Driven Programming · Clojure · Distributed Systems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer III} % Job title
    {Wizeline} % Organization
    {} % Location
    {Mar. 2021 - Jul. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on a platform that processed billions of events monthly for another one of the biggest broadcasting and entertainment companies in the US.}
        \item {Continue doing the tasks from my previous role.}
        \item {Skills: Event Driven Programming · Extract, Transform, Load (ETL) · Go · gRPC · Amazon Web Services (AWS)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer II} % Job title
    {} % Organization
    {} % Location
    {Nov. 2019 - Mar. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working on the Authorization/Identity flow for one of the biggest broadcasting companies in the U.S.}
        \item {Interview candidates continuously.}
        \item {Mentor newcomers and junior engineers to help them adopt best practices and develop their soft skills.}
        \item {Plan, organize, and execute initiatives to help community members to experience real interviews in a safe environment.}
        \item {Give courses and talks to the community about programming languages, trying to identify potential engineers and motivate them to start their journey in the IT industry.}
        \item {Contribute to internal development projects to improve different processes.}
        \item {Make continuing efforts to begin my career in Data Engineering/Science.}
        \item {Skills: Amazon Elasticsearch Service · Amazon Dynamodb · Go · Amazon Web Services (AWS) · Mentoring}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {} % Organization
    {} % Location
    {Nov. 2018 - Nov. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a chatbot for the biggest real estate company in the U.S.}
        \item {Contributed sporadically to the platform that manages all the chatbots in Wizeline.}
        \item {Gave courses to High School students to implement chatbots easily.}
        \item {Skills: Python · Microsoft Azure · MySQL · Flask}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Software Engineer Trainee} % Job title
    {} % Organization
    {} % Location
    {Aug. 2018 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as a Full-Stack Web Developer in the most used internal project. Developed significant new features and refactored a lot of legacy code.}
        \item {Promoted to a full-time position in two months.}
        \item {Skills: Node.js · React.js · MySQL}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
