%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Participant} % Degree
    {Saturdays.AI La Paz} % Institution
    {Guadalajara, Mexico} % Location
    {May. 2021 - Jul. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Attended Saturdays.AI La Paz Deep Learning edition where we continued developing our project "Violentómetro Online", which aims to detect hate-speech oriented towards women in texts found online.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Member of "Violentómetro-online Team"} % Affiliation/role
    {DataLab Community} % Organization/group
    {Guadalajara, Mexico} % Location
    {Jun. 2020 - Sep. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed a prototype to detect Spanish hate-speech against women.}
        \item {Won 3rd place against ~20 teams from all around Latin America.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Member of "Silver Team"} % Affiliation/role
    {Saturdays.AI Guadalajara} % Organization/group
    {Guadalajara, Mexico} % Location
    {Mar. 2020 - Jul. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed a project to estimate the correlation between Guadalajara's crimes and its public bike system.}
        \item {Contributed by always having high-quality code and enabled a distributed team to maintain it effectively.}
        \item {Won 3rd place in an internal contest against seven teams presenting their social-impact machine learning projects.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Judge} % Affiliation/role
    {Technovation Girls} % Organization/group
    {Guadalajara, Mexico} % Location
    {Apr. 2021 - May 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {I served as a judge for six different projects made by girls aged 10-18 years old. These projects aimed to solve a community problem by developing a mobile app.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Mentor} % Affiliation/role
    {} % Organization/group
    {} % Location
    {Feb. 2019 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Successfully mentored two teams, one at the High School level and the other one at the Jr. High School, to develop mobile applications to contribute to their community by solving social problems.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Data Analyst Volunteer} % Affiliation/role
    {University of Guadalajara} % Organization/group
    {Guadalajara, Mexico} % Location
    {Jan. 2018 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Analyzed data collected from students, looking to improve academic courses.}
        \item {Created a system that lets a user recollect data from surveys semi-automatically.}
        \item {Helped with managing courses and delivering homework notes to students.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
